Open Data

### 2020-05-30 draft_chapter.Rmd
refs update done

First, it is useful to clarify what we mean when we refer to 'open data'. The _Open Data Handbook_, compiled by the Open Knowledge Foundation, states that open data are "data that can be freely used, re-used and redistributed by anyone - subject only, at most, to the requirement to attribute and sharealike" [@dietrich2009open]. Specifically, open data can be defined along three key domains [@knowledge2016open].

>>>>

First, it is useful to clarify what we mean when we refer to 'open data'. The _Open Data Handbook_, compiled by the Open Knowledge Foundation, states that open data are "data that can be freely used, re-used and redistributed by anyone - subject only, at most, to the requirement to attribute and sharealike" [@dietrich2009open, para. 3]. Specifically, open data can be defined along three key domains [@knowledge2016open].
